\documentclass[a4paper,12pt]{article}

\title{Connect Forever: Design Document}
\author{Jolanda Verhoef \and Jaap Joris Vens}

\begin{document}
\maketitle

\section{Introduction}
Connect Forever is an Android app that allows two devices to connect and point to 
each other. 

\section{Functional Design}

\section{Technical Design}

Other Device Location
Starts thread that asks for other's location every x seconds

My Device Location
Starts gps updates. Tells the api the current location every x seconds

Location Service
Starts status updates. For now, status updates even when other location is
asked. Status is asked every y seconds.



States:
VIRGIN
PROPOSED
ENTERED
CONNECTED
OTHER_RESET
Service may only run in PROPOSED, CONNECTED states.

State transistions:

NONE -> VIRGIN
Application is downloaded from the market.
Status Service does not start immediately.
There is a (persistent) flag indicating if the user could become connected.
Program is started.
Virgin activity is shown.

  VIRGIN -> PROPOSED
  ENTERED -> PROPOSED
  User chooses "Propose".
  A proposal key is generated and shown (1).
  Status Service is started, flag set to true (persistently).
  User can check whether he/she is connected (2).
  
  (1) No key is returned from internet: appropriate error dialog is shown in
      virgin activity.
  (2) No response from internet: appropriate error dialog is shown in
      ShowProposal activity.
  
    PROPOSED -> CONNECTED
    Other device connects while program is active.
    Program is in this case always in ShowProposal activity.
    User clicks on "Connect" - API returns connected (1).
    Main Activity is shown with Hooray message in front of it.
    
    (1) Alternatively, the service returns connected, same happens.
    
    PROPOSED -> CONNECTED
    Other device connects while program is inactive.
    Service notices, can show notification (?).
    When program is started, should go to Main Activity with Hooray message.
  
    PROPOSED -> ENTERED / VIRGIN
    User selects "Withdraw proposal" (1).
    Show Proposal Activity is closed.
    
    (1) No internet -> error dialog.
    
  VIRGIN -> ENTERED
  User chooses "Enter proposal".
  An edit text is available to enter key (key is remembered persistently!).
  User enters key -> any letters gives ENTERED state, unless currently in
  PROPOSED state.
  
  ENTERED -> CONNECTED
  User clicks "Connect".
  Key is checked by API, returns "Congratulations" when connected (1).
  Hooray message is shown, after OK the Main Activity is shown.
  
  (1) Problem occurs, user is notified by error dialog.
  

Precondition: State is CONNECTED

States:
NONE
STATUS_UPDATES
LOCATION_PUSHING
+ LOCATION_PULLING

... -> + LOCATION_PULLING
Precondition: state is CONNECTED
Starting Main Activity starts LOCATION_PULLING (1)

(1) If no connection -> User notified by error dialog.

... -> - LOCATION_PULLING
Stopping Main Activity stops LOCATION_PULLING.

NONE -> STATUS_UPDATES
Internet connection is established

Status Service is running.

CONNECTED -> OTHER_RESET -> VIRGIN
Status Service receives "Not Connected" (other device resetted app)
State is set to "OTHER_RESET", Main Activity will show Error dialog (either
direct, or when program is started)
OK leads to VIRGIN state.

Status Service receives "Inactive", does nothing special

STATUS_UPDATES -> LOCATION PUSHING
Status Service receives "Active", starts LOCATION_PUSHING, stops
STATUS_UPDATES.

LOCATION_PUSING -> STATUS_UPDATES
Status Service receives "Thank you", starts STATUS_UPDATES, stops
LOCATION_PUSHING.

... -> NONE
Internet connection fails (API request returns Exception).
Status Service responds by stopping itself.
LOCATION_PULLING responds by showing error dialog.


\section{Technical Design}
\subsection{Web API}
\subsection{Android App}
